### 2013-09-29 tex/scam/optimization.tex
various edits. Added new mean parameter to opti

We consider the following nonparametric regression problem
\begin{equation}\nonumber
          y_{i} = f(\bds{x}_{i}) + \epsilon_{i} = \sum_{k=1}^{p}f_{k}(x_{ki}) + \epsilon_{i} \quad i=1,2,\cdots,n
\end{equation}
where $\bds{x}_{i}\in\mathbb{R}^{p}$ is the covariate, $y_{i}$ is the
response and $\epsilon_{i}$ is mean zero noise. The regression function $f(\cdot)$ is the summation of 
functions $f_{k}(\cdot)$ in each variable dimension.  
We impose an additional constraint that each $f_{k}(\cdot)$ is 
an univariate convex function, which can be represented by its supporting hyperplanes, i.e.,
\begin{equation}\label{hyper}
      h_{kj} \geq h_{ki} + \beta_{ki}(x_{kj}-x_{ki}) \quad (\forall i,j)
\end{equation}
where $h_{ki}\coloneqq f_{k}(x_{ki})$ and $\beta_{ki}$ is the
subgradient at point $x_{ki}$. We apparently need $O(n^2 p)$ constraints to
impose the supporting hyperplane constraints, which is computationally
expensive for large scale problems.  In fact, only $O(np)$
constraints suffice, since univariate convex functions are
characterized by the condition that the subgradient, which is a scalar, must
increase monotonically. This observation leads to our optimization
program:
\begin{equation}\begin{split}\label{np}
       &\min_{\bds{h},\bds{\beta}} \ \frac{1}{2n}\sum_{i=1}^{n}\Bigl(y_{i}-\sum_{k=1}^{p}h_{ki}\Bigr)^{2} + \lambda\sum_{k=1}^{p}\|\bds{\beta}_{k\cdot}\|_{\infty} \\
       &\ \textrm{s.t.} \ \sum_{i=1}^{n}h_{ki}=0,\; h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}), \ \beta_{k(i+1)} \geq \beta_{k(i)} \ (\forall k, i)
\end{split}\end{equation}
Let $\{(1),(2),\ldots,(n)\}$ be a reordering of $\{1,2,\ldots,n\}$ such that $x_{k(1)}\leq{}x_{k(2)}\leq\cdots\leq{}x_{k(n)}$.  It is easy to verify that the constraints in (\ref{np}) satisfy the supporting hyperplane constraints, as
\begin{eqnarray}
  \nonumber \forall j\geq{}i, &h_{k(j)}-h_{k(i)}  = \sum\limits_{t=i}^{j-1}(h_{k(t+1)}-h_{k(t)}) = \sum\limits_{t=i}^{j-1}\beta_{k(t)}(x_{k(t+1)}-x_{k(t)})\\ \nonumber
                                                                             & \geq \beta_{k(i)}\sum\limits_{t=i}^{j-1}(x_{k(t+1)}-x_{k(t)}) = \beta_{k(i)}(x_{k(j)}-x_{k(i)}) \\
  \nonumber \forall j<i,         &h_{k(j)}-h_{k(i)} = \sum\limits_{t=j}^{i-1}(h_{k(t)}-h_{k(t+1)}) = \sum\limits_{t=j}^{i-1}\beta_{k(t)}(x_{k(t)}-x_{k(t+1)}) \\ \nonumber
                                                                             & \geq \beta_{k(i)}\sum\limits_{t=j}^{i-1}(x_{k(t)}-x_{k(t+1)}) = \beta_{k(i)}(x_{k(j)}-x_{k(i)}), 
\end{eqnarray}
The $\ell_\infty/\ell_1$ penalty
$\sum_{k=1}^{p}\|\bds{\beta}_{k\cdot}\|_{\infty}$ encourages group
sparsity of the vectors $\bds{\beta}_{k\cdot}$, and thus performs
variable selection.  We refer to this framework as the sparse convex
additive model (SCAM). Notice that if we replace $\beta_{k(i+1)} \geq
\beta_{k(i)}$ with $\beta_{k(i+1)}=\beta_{k(i)}$, the optimization
reduces to the lasso.  Note while one can use
supporting hyperplanes to the epigraph as in \eqref{eq:outer}, 
SCAM uses the \emph{inner  piece-wise linear function}
that approximates the graph with secant lines.

@@

The SCAM optimization in (\ref{np}) is a quadratic program (QP) with $O(np)$ variables and $O(np)$ constraints. 
Directly applying a QP solver would be computationally expensive for relatively large $n$ and $p$. However, notice that variables
in different feature dimensions are only coupled in the term $(y_{i}-\sum_{k=1}^{p}h_{ki})^{2}$. Hence, we can apply the block coordinate descent method,
where in each step we solve the following QP subproblem for
$\{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot}\}$ with the other variables fixed:
\begin{equation}\begin{split}\nonumber
       &\min_{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot},\gamma_{k}} \ \frac{1}{2n}\sum_{i=1}^{n}\Bigl((y_{i}-\sum_{r\neq{k}}h_{ri})-h_{ki}\Bigr)^{2} + \lambda\gamma_{k} \\
        &\ \textrm{s.t.} \ \sum_{i=1}^{n}h_{ki}=0, \ h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}), \ \beta_{k(i+1)} \geq \beta_{k(i)}, \ -\gamma_{k}\leq\beta_{k(i)}\leq\gamma_{k} \ (\forall i).
\end{split}\end{equation}
The extra variable $\gamma_{k}$ is introduced to deal with the $\ell_{\infty}$ norm. This QP subproblem involves $O(n)$ variables, $O(n)$ constraints and a sparse structure, 
which can be solved efficiently using optimization packages (e.g., MOSEK: \verb+http://www.mosek.com/+).  We cycle through all feature dimensions ($k$) from $1$ to $p$ multiple times until convergence.
Empirically, we observe that the algorithm converges in only a few cycles. We also implemented an ADMM solver for (\ref{np}), but found that it is not as efficient as this QP solver.

After optimization, the function estimator for any input data $\bds{x}_j$ is, according to (\ref{hyper}),
\begin{equation}\nonumber
      f(\bds{x}_j) = \sum_{k=1}^{p}f_k(x_{kj}) = \sum_{k=1}^{p}\max_{i} \{h_{ki}+\beta_{ki}(x_{kj}-x_{ki})\}.
\end{equation}

%% Why hats here?  Turning them off (JDL)
\def\hat#1{#1}

\subsection{Alternative Formulation}
Optimization (\ref{np}) can be reformulated in terms of the 2nd derivatives. The alternative formulation replaces the ordering
constraints $\beta_{k(i+1)} \geq \beta_{k(i)}$ with positivity
constraints, which simplifies theoretical analysis.
Define $\hat{d}_{k(i)}$ as the gradient increment:
$\hat{d}_{k(1)} = \hat{\beta}_{k(1)}$, and $\hat{d}_{k(2)} =
\hat{\beta}_{k(2)} - \hat{\beta}_{k(1)}$. The convexity constraint is
equivalent to the constraint that $\hat{d}_{k(i)} \geq 0$ for all $i >
1$.

It is easy to verify that $\hat{\beta}_{k(i)} = \sum_{j \leq i} \hat{d}_{k(i)}$ and 
\[
\hat{f}_k(x_{k(i)}) = \hat{f}_k({x_{k(1)}}) +\hat{d}_{k(1)} ( x_{k(i)}
- x_{k(1)}) + \hat{d}_{k(2)} ( x_{k(i)} - x_{k(2)}) + \cdots + \hat{d}_{k(i-1)} ( x_{k(i)} - x_{k(i-1)})
\]
Define $\Delta(j, x_{ki}) = 0$ if $\trm{ord}(i) \leq j$, and
$\Delta(j,x_{ki})= x_{ki} -
x_{k(j)}$ otherwise, where $j$ ranges from $1$ to $n-1$.  Also define
$\Delta(x_{ki}) = \{ \Delta(j, x_{ki}) \}_{j=1, \ldots ,n-1}$ as an
$n-1$ dimensional vector. Then $\hat{f}_k(x_{ki}) = \Delta(x_{ki})^\tran \hat{d}_{k}$ where $\Delta(x_{ki}) \in \R^{n-1}$. Given $n$ samples $\{x_{ki}\}_{i=1}^n$, we can further define $\Delta_k \in \R^{n \times n-1}$ such that the $i$-th row is $\Delta(x_{ki})$. Finally, we reformulate (\ref{np}) as an equivalent optimization program with only centering and positivity constraints:
\begin{align}
\min_{\{d_k \in \R^{n-1}, c_k \in \R\}}& \frac{1}{2n} \Bigl\| Y - \sum_{k=1}^p ( \Delta_k d_k - c_k \mathbf{1}_n) \Bigr\|_2^2 + \lambda_n \sum_{k=1}^p \|d_k\|_1  & \label{opt:alternate_opt} \\
\trm{s.t. $\forall k$, }  & d_{k2}, \ldots , d_{k(n-1)} \geq 0 	\qquad &\trm{(convexity)} \nonumber \\ 
	& c_k = \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k 	\qquad &\trm{(centering)} \nonumber 
\end{align}
$\|d_k\|_1$ is not identical to $\|\bds{\beta}_{k\cdot}\|_{\infty}$, but it is easy to verify that $\|\bds{\beta}_{k\cdot}\|_{\infty} \leq \|d_k\|_1 \leq 2\|\bds{\beta}_{k\cdot}\|_{\infty}$.

\begin{remark}
\label{rem:bounded_lipschitz_constraints}
For parts of our theoretical analysis, we will also impose onto (\ref{opt:alternate_opt}) a boundedness constraint $-B \mathbf{1}_n \leq \Delta_k d_k + c_k \mathbf{1}_n \leq B \mathbf{1}_n$ which constrains that $\|\hat{f}_k \|_\infty \leq B$, or a Lipschitz constraint $\|d_k\|_1 \leq L$ which constrains that $\hat{f}_k$ must be $L$-Lipschitz. We use these constraints only in the proof for technical reasons; we never need nor use these constraints in our experiments.
\end{remark}

%% turn the hat back on (JDL)
\def\hat#1{\widehat{#1}}

>>>>

We consider the following nonparametric regression problem
\begin{equation}\nonumber
          y_{i} = f(\bds{x}_{i}) + \epsilon_{i} = 
                  \sum_{k=1}^{p}f_{k}(x_{ki}) + \epsilon_{i} \quad i=1,2,\cdots,n
\end{equation}
where $\bds{x}_{i}\in\mathbb{R}^{p}$ is the covariate, $y_{i}$ is the
response and $\epsilon_{i}$ is mean zero noise. The regression function $f(\cdot)$ is the summation of 
functions $f_{k}(\cdot)$ in each variable dimension.  
We impose an additional constraint that each $f_{k}(\cdot)$ is 
an univariate convex function, which can be represented by its supporting hyperplanes, i.e.,
\begin{equation}\label{hyper}
      h_{kj} \geq h_{ki} + \beta_{ki}(x_{kj}-x_{ki}) \quad (\forall i,j)
\end{equation}
where $h_{ki}\coloneqq f_{k}(x_{ki})$ and $\beta_{ki}$ is the
subgradient at point $x_{ki}$. We apparently need $O(n^2 p)$ constraints to
impose the supporting hyperplane constraints, which is computationally
expensive for large scale problems.  In fact, only $O(np)$
constraints suffice, since univariate convex functions are
characterized by the condition that the subgradient, which is a scalar, must
increase monotonically. This observation leads to our optimization
program:
\begin{equation}\begin{split}\label{np}
       &\min_{\bds{h},\bds{\beta},\mu} \ \frac{1}{2n}\sum_{i=1}^{n}
                     \Bigl( y_{i}-\sum_{k=1}^{p}h_{ki} - \mu \Bigr)^{2} 
                         + \lambda\sum_{k=1}^{p}\|\bds{\beta}_{k\cdot}\|_{\infty} \\
       &\ \textrm{s.t.} \ \sum_{i=1}^{n}h_{ki}=0,\; h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}), 
                                 \ \beta_{k(i+1)} \geq \beta_{k(i)} \ (\forall k, i)
\end{split}\end{equation}
Where $\mu \in \R$ is a mean parameter introduced because $f$ may not have zero-mean, and where $\{(1),(2),\ldots,(n)\}$ is a reordering of $\{1,2,\ldots,n\}$ such that $x_{k(1)}\leq{}x_{k(2)}\leq\cdots\leq{}x_{k(n)}$.  It is easy to verify that the constraints in (\ref{np}) satisfy the supporting hyperplane constraints, as
\begin{align*}
  \forall j\geq{}i, &h_{k(j)}-h_{k(i)}  = 
            \sum\limits_{t=i}^{j-1}(h_{k(t+1)}-h_{k(t)}) = 
            \sum\limits_{t=i}^{j-1}\beta_{k(t)}(x_{k(t+1)}-x_{k(t)})\\ 
      & \geq \beta_{k(i)}\sum\limits_{t=i}^{j-1}(x_{k(t+1)}-x_{k(t)}) = \beta_{k(i)}(x_{k(j)}-x_{k(i)}) \\
  \forall j<i, &h_{k(j)}-h_{k(i)} =
                \sum\limits_{t=j}^{i-1}(h_{k(t)}-h_{k(t+1)}) = 
                \sum\limits_{t=j}^{i-1}\beta_{k(t)}(x_{k(t)}-x_{k(t+1)}) \\ 
     & \geq \beta_{k(i)}\sum\limits_{t=j}^{i-1}(x_{k(t)}-x_{k(t+1)}) = \beta_{k(i)}(x_{k(j)}-x_{k(i)}), 
\end{align*}
The $\ell_\infty/\ell_1$ penalty
$\sum_{k=1}^{p}\|\bds{\beta}_{k\cdot}\|_{\infty}$ encourages group
sparsity of the vectors $\bds{\beta}_{k\cdot}$, and thus performs
variable selection.  We refer to this framework as the sparse convex
additive model (SCAM). Notice that if we replace $\beta_{k(i+1)} \geq
\beta_{k(i)}$ with $\beta_{k(i+1)}=\beta_{k(i)}$, the optimization
reduces to the lasso.  Note while one can use
supporting hyperplanes to the epigraph as in \eqref{eq:outer}, 
SCAM uses the \emph{inner  piece-wise linear function}
that approximates the graph with secant lines.

@@

The SCAM optimization in (\ref{np}) is a quadratic program (QP) with $O(np)$ variables and $O(np)$ constraints. The optimal $\mu$ has a closed form solution of $\mu = \frac{1}{n}\sum_{i=1}^n Y_i$, which is easy to derive from the KKT theorem and the constraints that $\sum_i h_{ki} = 0$ for all $k$.
Directly applying a QP solver for $\bds{h}, \bds{\beta}$ would be computationally expensive for relatively large $n$ and $p$. However, notice that variables
in different feature dimensions are only coupled in the term $(y_{i}-\sum_{k=1}^{p}h_{ki})^{2}$. Hence, we can apply the block coordinate descent method,
where in each step we solve the following QP subproblem for
$\{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot}\}$ with the other variables fixed:
\begin{equation}\begin{split}\nonumber
       &\min_{\bds{h}_{k\cdot},\bds{\beta}_{k\cdot},\gamma_{k}} 
                       \ \frac{1}{2n}\sum_{i=1}^{n}\Bigl((y_{i}-\sum_{r\neq{k}}h_{ri}-\mu)-h_{ki}\Bigr)^{2} 
                         + \lambda\gamma_{k} \\
        &\ \textrm{s.t.} \ \sum_{i=1}^{n}h_{ki}=0, \ h_{k(i+1)} = h_{k(i)} + \beta_{k(i)}(x_{k(i+1)}-x_{k(i)}), \ \beta_{k(i+1)} \geq \beta_{k(i)}, \ -\gamma_{k}\leq\beta_{k(i)}\leq\gamma_{k} \ (\forall i).
\end{split}\end{equation}
The extra variable $\gamma_{k}$ is introduced to deal with the $\ell_{\infty}$ norm. This QP subproblem involves $O(n)$ variables, $O(n)$ constraints and a sparse structure, 
which can be solved efficiently using optimization packages (e.g., MOSEK: \verb+http://www.mosek.com/+).  We cycle through all feature dimensions ($k$) from $1$ to $p$ multiple times until convergence.
Empirically, we observe that the algorithm converges in only a few cycles. We also implemented an ADMM solver for (\ref{np}), but found that it is not as efficient as this QP solver.

After optimization, the function estimator for any input data $\bds{x}_j$ is, according to (\ref{hyper}),
\begin{equation}\nonumber
      f(\bds{x}_j) = \sum_{k=1}^{p}f_k(x_{kj})+\mu = \sum_{k=1}^{p}\max_{i} \{h_{ki}+\beta_{ki}(x_{kj}-x_{ki})\} + \mu.
\end{equation}

\subsection{Alternative Formulation}
Optimization (\ref{np}) can be reformulated in terms of the 2nd derivatives. The alternative formulation replaces the ordering
constraints $\beta_{k(i+1)} \geq \beta_{k(i)}$ with positivity
constraints, which simplifies theoretical analysis.
Define $d_{k(i)}$ as the second derivative:
$d_{k(1)} = \beta_{k(1)}$, and $d_{k(2)} =
\beta_{k(2)} - \beta_{k(1)}$. The convexity constraint is
equivalent to the constraint that $d_{k(i)} \geq 0$ for all $i >
1$.

It is easy to verify that $\beta_{k(i)} = \sum_{j \leq i} d_{k(i)}$ and 
\[
f_k(x_{k(i)}) = f_k({x_{k(1)}}) +d_{k(1)} ( x_{k(i)}
- x_{k(1)}) + d_{k(2)} ( x_{k(i)} - x_{k(2)}) + \cdots + d_{k(i-1)} ( x_{k(i)} - x_{k(i-1)})
\]
Define $\Delta(j, x_{ki}) = 0$ if $\trm{ord}(i) \leq j$, and
$\Delta(j,x_{ki})= x_{ki} -
x_{k(j)}$ otherwise, where $j$ ranges from $1$ to $n-1$.  Also define
$\Delta(x_{ki}) = \{ \Delta(j, x_{ki}) \}_{j=1, \ldots ,n-1}$ as an
$n-1$ dimensional vector. Then $f_k(x_{ki}) = \Delta(x_{ki})^\tran d_{k}$ where $\Delta(x_{ki}) \in \R^{n-1}$. Given $n$ samples $\{x_{ki}\}_{i=1}^n$, we can further define $\Delta_k \in \R^{n \times n-1}$ such that the $i$-th row is $\Delta(x_{ki})$. Finally, we reformulate (\ref{np}) as an equivalent optimization program with only centering and positivity constraints:
\begin{align}
\min_{d_k \in \R^{n-1}, c_k \in \R,\mu \in \R}& \frac{1}{2n} 
               \Bigl\| Y - \sum_{k=1}^p ( \Delta_k d_k - c_k \mathbf{1}_n) -\mu \Bigr\|_2^2 
               + \lambda_n \sum_{k=1}^p \|d_k\|_1  & \label{opt:alternate_opt} \\
\trm{s.t. $\forall k$, }  & d_{k2}, \ldots , d_{k(n-1)} \geq 0 	\qquad &\trm{(convexity)} \nonumber \\ 
	& c_k = \frac{1}{n} \mathbf{1}_n^\tran \Delta_k d_k 	\qquad &\trm{(centering)} \nonumber 
\end{align}
$\|d_k\|_1$ is not identical to $\|\bds{\beta}_{k\cdot}\|_{\infty}$, but it is easy to verify that $\|\bds{\beta}_{k\cdot}\|_{\infty} \leq \|d_k\|_1 \leq 2\|\bds{\beta}_{k\cdot}\|_{\infty}$.

\begin{remark}
\label{rem:bounded_lipschitz_constraints}
For parts of our theoretical analysis, we will also impose onto (\ref{opt:alternate_opt}) a boundedness constraint $-B \mathbf{1}_n \leq \Delta_k d_k + c_k \mathbf{1}_n \leq B \mathbf{1}_n$ which constrains that $\|f_k \|_\infty \leq B$, or a Lipschitz constraint $\|d_k\|_1 \leq L$ which constrains that $f_k$ must be $L$-Lipschitz. We use these constraints only in the proof for technical reasons; we never need nor use these constraints in our experiments.
\end{remark}

### 2013-09-29 tex/scam/sparsistency.tex
various edits. Added new mean parameter to opti

Our analysis then diverges from the now-standard ``primal-dual witness
technique''~\cite{Wain:09a}. Primal-dual witness explicitly solves all the dual variables. Because our optimization is more complex, we do not solve the dual variables on $S$, we instead write the dual variables on $S^c$ as a function of the restricted regression \emph{residual}, which is implicitly a function of the dual variables on $S$.

\begin{theorem} (Deterministic setting)
\label{thm:deterministic}
Let $\{\hat{d}_k, \hat{c}_k \}_{k \in S}$ be the minimizer of the restricted regression, that is, the solution to optimization (\ref{opt:alternate_opt}) where we restrict $k \in S$. Let $\hat{d}_k = 0$ and $ \hat{c}_k = 0$ for $k \in S^c$.
Let $\hat{r} \coloneqq Y - \sum_{k \in S} (\Delta_k \hat{d}_k -
\hat{c}_k \mathbf{1})$ be the restricted regression residual. For $k
\in \{1,...,p\}$, $\Delta_{k, j}$, the $j$-th column of $\Delta_k$, is the $n$-dimensional vector $\max( X_k - X_{k (j)} \mathbf{1}, 0)$. 
Suppose for all $j$ and all $k\in S^c$, $\lambda_n > | \frac{1}{n}
\hat{r}^\tran \Delta_{k,j}|$. Then $\hat{d}_k, \hat{c}_k$ for $k=1,...,p$ is an optimal solution to the full regression \ref{opt:alternate_opt}. Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
\end{theorem}
This result holds regardless of whether we impose the boundness and Lipschitz conditions in optimization~\ref{opt:alternate_opt}.
The full proof of Theorem~\ref{thm:deterministic} is in Section~\ref{sec:deterministic_proof} of the Appendix.

@@

\begin{packed_enum}
\item Let $\mathcal{X} = [-b, b]^p$. Let $F$ be a distribution supported and positive on $\mathcal{X}$. Let $X^{(1)},..., X^{(n)} $ be independent samples from $F$. 
\item Let $Y' = f_0(X) + \epsilon$ where $f_0$ is the true function and $\epsilon$ is noise.  Given $n$ samples $Y'^{(1)},...,Y'^{(n)}$, we input into our optimization $Y = Y' - \bar{Y}'$.
\item Let $S \subset \{1,...,p\}$ denote the relevant variables, i.e.,
  $f_0(X) = f_0(X_S)$, with $s \coloneqq |S|$. 
\end{packed_enum}

Each of our statistical theorems will use a subset of the following assumptions:
\begin{packed_enum}
\item[A1:] $X_S, X_{S^c}$ are independent.  \ A1': $\{ X_k \}_{k \in S}$ are independent.
\item[A2:] $\|f_0\|_\infty \leq B$. \  A2': $f_0$ is convex,
  twice-differentiable, $L$-Lipschitz, and $\trm{supp}(f_0) = S$.
\item[A3:] Suppose $\epsilon$ is mean-zero sub-Gaussian, independent of $X$, with sub-Gaussian scale $\sigma$.
\end{packed_enum}

We will use assumptions A1, A2, A3 to control the probability of false positives and the stronger assumptions A1', A2', A3 to control the probability of false negatives.

>>>>

Our analysis then diverges from the now-standard ``primal-dual witness
technique''~\cite{Wain:09a}. Primal-dual witness explicitly solves all the dual variables, but because our optimization is more complex, we do not solve the dual variables on $S$; we instead write the dual variables on $S^c$ as a function of the restricted regression \emph{residual}, which is implicitly a function of the dual variables on $S$.

\begin{theorem} (Deterministic setting)
\label{thm:deterministic}
Let $\{\hat{d}_k, \hat{c}_k, \hat{\mu} \}_{k \in S}$ be the minimizer of the restricted regression, that is, the solution to optimization (\ref{opt:alternate_opt}) where we restrict $k \in S$. Let $\hat{d}_k = 0$ and $ \hat{c}_k = 0$ for $k \in S^c$.
Let $\hat{r} \coloneqq Y - \sum_{k \in S} (\Delta_k \hat{d}_k -
\hat{c}_k \mathbf{1}) - \hat{\mu}$ be the restricted regression residual. For $k
\in \{1,...,p\}$, $\Delta_{k, j}$, the $j$-th column of $\Delta_k$, is the $n$-dimensional vector $\max( X_k - X_{k (j)} \mathbf{1}, 0)$. 
Suppose for all $j$ and all $k\in S^c$, $\lambda_n > | \frac{1}{n}
\hat{r}^\tran \Delta_{k,j}|$. Then $\hat{d}_k, \hat{c}_k$ for $k=1,...,p$ is an optimal solution to the full regression \ref{opt:alternate_opt}. Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
\end{theorem}
This result holds regardless of whether we impose the boundness and Lipschitz conditions in optimization~\ref{opt:alternate_opt}.
The full proof of Theorem~\ref{thm:deterministic} is in Section~\ref{sec:deterministic_proof} of the Appendix.

@@

\begin{packed_enum}
\item Let $\mathcal{X} = [-b, b]^p$. Let $F$ be a distribution supported and positive on $\mathcal{X}$. Let $X^{(1)},..., X^{(n)} $ be independent samples from $F$. 
\item Let $Y = f_0(X) + \epsilon$ where $f_0$ is the true function and $\epsilon$ is noise. Let $Y^{(1)},...,Y^{(n)}$ be $n$ samples of $Y$.
\item Let $s \leq p$ be a positive integer. Let $S = \{1,...,s\}$ denote the relevant variables, i.e.,
  $f_0(X) = f_0(X_S)$.
\item Let $f_{01},...,f_{0s} \coloneqq \argmin_{f_1,...,f_s} \{ \E(f_0(X) - \sum_{k=1}^s f_k(X_k) -\mu )^2 \,|\, \E[f_k(X_k)] = 0 \}$ where $\mu = \Ef(X)$.
\end{packed_enum}

Each of our statistical theorems will use a subset of the following assumptions:
\begin{packed_enum}
\item[A1:] $X_S, X_{S^c}$ are independent.  \ A1': $\{ X_k \}_{k \in S}$ are independent.
\item[A2:] $\|f_0\|_\infty \leq sB$ \  A2': $f_0$ is convex,
  twice-differentiable, $L$-Lipschitz, and $\trm{supp}(f_0) = S$.
\item[A3:] Suppose $\epsilon$ is mean-zero sub-Gaussian, independent of $X$, with sub-Gaussian scale $\sigma$.
\item[A4:] For all $k=1,...,s$, $\E(f_{0k}(X_k))^2 \geq \alpha$ for some positive constant $\alpha$.
\end{packed_enum}

We will use assumptions A1, A2, A3 to control the probability of false positives and the stronger assumptions A1', A2', A3, A4 to control the probability of false negatives.
